Quality Definitions of Qualities

### 2021-10-06 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Completed the quality of performance, explicitly indicated \notdone{}

\subsection{Reliability (external, product, process)} %\oo{owner} %NOTDONE

@@

Definition \ref{reliabilitySelected1} and \ref{reliabilitySelected2} rephrased:.
Reliability is defined such that the measurement metrics are visible - the
specified environment and time.   The different reasons for the proposed
definition are as follows:

@@

\subsection{Robustness (external, product, process)} %\pmi{owner}

@@

\begin{defn}
	In software engineering we often equate performance with efficiency. A
  software system is efficient if it uses computing resources economically
  \citep{ghezzi1991fundamentals}.  \wss{Change to 2003 reference?}
\end{defn}

@@

\begin{mybox}
\subsubsection*{Performance}
The degree to which a system or component accomplishes its designated functions
within given constraints, such as speed (database response times, for instance),
throughput (transactions per second), capacity (concurrent usage loads), and
timing (hard real-time demands).
\wss{What is the difference between speed and timing?}
\end{mybox}

@@

The definition is found by combining Definition~\ref{PerformanceDefnSelected}
and Definition~\ref{PerformanceDefnSelected2}.  This definition offers a
comprehensive list of constraints that are commonly associated with software
performance, such as speed, throughput, capacity, and timing. \pmi{I will check
if Wiegers discusses the difference between speed and timing.} \pmi{Wiegers did
not discuss this difference.}  \pmi{Speed - change over time; timing - related
to specification: when something should happen in relation to something else -
state transitions}  \wss{If we need both speed and timing, we should define
them.  We aren't including accuracy from the IEEE definition.  Is that on
purpose?}  \pmi{We have decided not to include accuracy. SS will find difference
b/w speed and timing from a colleague.}   The different reasons for the proposed
definition are as follows:

@@

\subsection{Usability (external, product, process) } %\notdone \jc{owner}

@@

\subsection{Verifiability (internal, product, process) } %\notdone \oo{owner}

@@

\subsection{Validatability (external, product, process)} %\notdone \oo{owner}

@@

\subsection{Testability (internal, product)} %\notdone \oo{owner}

@@

\subsection{Maintainability (internal, product, process)} %\notdone \pmi{owner}

@@

\subsection{Reusability (internal, product, process)} %\pmi{owner}

@@

\subsection{Portability (internal, product)} %\pmi{owner}

@@

\subsection{Understandability (internal, product)} %\notdone \jc{owner}

@@

\subsection{Interoperability (external, product)} %\notdone \ad{owner}

@@

\subsection{Productivity (process)} %\notdone \ad{owner}}

@@

\subsection{Visibility/Transparency (process)} %\notdone \ad{owner}

@@

\subsection{Reproducibility (external, product)} %\notdone \wss{owner}

@@

\subsection{Sustainability (internal, product)} %\notdone \wss{owner}

@@

\subsection{Completeness} %\ontdone \ad{owner}

@@

\subsection{Consistency} %\notdone \ad{owner}

@@

\subsection{Modifiability} %\notdone \jc{owner}

@@

\subsection{Traceability} %\notdone \jc{owner}

@@

\subsection{Unambiguity} %\notdone \wss{owner}

@@

\subsection{Abstract} %\notdone \wss{owner}

>>>>

\subsection{\notdone{Reliability (external, product, process)}} %\oo{owner} %NOTDONE

@@

Definition \ref{reliabilitySelected1} and \ref{reliabilitySelected2} rephrased:.
Reliability is defined such that the measurement metrics are visible - the
specified environment and time.   \wss{Accuracy should be mentioned here, since
it is related to how close the solution is to the correct solution.  Accuracy is
not part of performance.  Maybe make accuracy part of correctness?}  The
different reasons for the proposed definition are as follows:

@@

\subsection{\notdone{Robustness (external, product, process)}} %\pmi{owner}

@@

\begin{defn} \label{PerformanceGhezzieEtAl2003}
	Performance ... is an external quality based on user requirements.
  \citep[p.\ 20]{GhezziEtAl2003}.
\end{defn}

@@

\begin{mybox}
\subsubsection*{Performance}
The extent to which a system or component accomplishes its functional
requirements within the given constraints of speed (database response times,
for instance), throughput (transactions per second), capacity (concurrent usage
loads), and timing (hard real-time demands).
\end{mybox}

@@

The definition is found by combining Definition~\ref{PerformanceDefnSelected}
and Definition~\ref{PerformanceDefnSelected2}.  The two definitions are fairly
similar.  We liked the structure of Definition~\ref{PerformanceDefnSelected} and
the more detailed list of performance aspects in
Definition~\ref{PerformanceDefnSelected2}.  The specific reasons for the
proposed definition are as follows:

\begin{itemize}
  \item We say ``the extent to which'' to be consistent with our other
  definitions.
  \item We changed ``designated functions'' to ``functional requirements'' for
  the goal of being unambiguous.  We already introduced the distinction between
  functional and nonfunctional requirements in the discussion of correctness.
  This also connects the proposed definition to the user requirements, as is
  done by Definition~\ref{PerformanceGhezzieEtAl2003}.
  \item To remove ambiguity, we explicitly list all aspects of performance
  (speed, throughput, capacity and timing), instead of introducing a list that
  is implied to be incomplete via the phrase ``such as''.
  \item We do not include accuracy (from
  Definition~\ref{PerformanceDefnSelected}) because we consider accuracy to be
  related to correctness and reliability.
\end{itemize}

@@

\subsection{\notdone{Usability (external, product, process)}} %\notdone \jc{owner}

@@

\subsection{\notdone{Verifiability (internal, product, process)}} %\notdone \oo{owner}

@@

\subsection{\notdone{Validatability (external, product, process)}} %\notdone \oo{owner}

@@

\subsection{\notdone{Testability (internal, product)}} %\notdone \oo{owner}

@@

\subsection{\notdone{Maintainability (internal, product, process)}} %\notdone \pmi{owner}

@@

\subsection{\notdone{Reusability (internal, product, process)}} %\pmi{owner}

@@

\subsection{\notdone{Portability (internal, product)}} %\pmi{owner}

@@

\subsection{\notdone{Understandability (internal, product)}} %\notdone \jc{owner}

@@

\subsection{\notdone{Interoperability (external, product)}} %\notdone \ad{owner}

@@

\subsection{\notdone{Productivity (process)}} %\notdone \ad{owner}}

@@

\subsection{\notdone{Visibility/Transparency (process)}} %\notdone \ad{owner}

@@

\subsection{\notdone{Reproducibility (external, product)}} %\notdone \wss{owner}

@@

\subsection{\notdone{Sustainability (internal, product)}} %\notdone \wss{owner}

@@

\subsection{\notdone{Completeness}} %\ontdone \ad{owner}

@@

\subsection{\notdone{Consistency}} %\notdone \ad{owner}

@@

\subsection{\notdone{Modifiability}} %\notdone \jc{owner}

@@

\subsection{\notdone{Traceability}} %\notdone \jc{owner}

@@

\subsection{\notdone{Unambiguity}} %\notdone \wss{owner}

@@

\subsection{\notdone{Abstract}} %\notdone \wss{owner}
